---
title: "{{{report_title}}}"
subtitle: "Start here when making deliverables with MS Word"
author: "{{{author}}}"
date: "Document created on `r format(Sys.time(), '%B %d, %Y')`" 
bibliography: refs.bib
csl: refs.csl
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: perisphere_template.docx
    keep_md: true
    toc: true
    toc_depth: 2
---

```{r setup-knitr, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,    # don't show code blocks
  message = FALSE, # don't print messages to the doc
  warning = FALSE, # don't print warnings to the doc
  dpi = 300,       # higher dpi => higher render time 
  fig.width = 6,   # default figure width in inches
  fig.height = 4   # default figure height in inches
)

# Hello! This is the template word document for Perisphere reports.
# There are several code chunks used to set up the format of the
# document below. You don't have to modify those unless you want 
# to change the format of your output. 

```

```{r setup-pkgs}

# packages are usually handled by packages.R (in main directory).
# When tar_make() is run, it loads everything in packages.R.
# Assuming this document is in the list of targets (see ?tar_render),
# you won't need to include the library calls below.
# however, the template includes packages in its initial form
# so that you can knit the document without having to run tar_make()

# standards for word docs
library(officer)
library(flextable)

# specify a rounding specification 
library(periglue)

# general purpose
library(tidyverse)
library(pericircle)

# table 1
library(gtsummary)

```

```{r setup-figures}

set_fig_landscape <- function() {
  knitr::opts_chunk$set(fig.width = 11, fig.height = 6)
}

set_fig_portrait <- function() {
  knitr::opts_chunk$set(fig.width = 6, fig.height = 4)
}

theme_set(
  new = theme_bw() + 
    theme(panel.grid = element_blank(),
          text = element_text(size = 12))
)

```

```{r setup-margins}

# Set a default footer because when we use block_section, it 
# starts a new style template for headers and footers. Thus,
# if we want page numbers to appear on every page, we need to
# put that into the default footer and then put that default
# footer into every block section. MS word...¯\_(ツ)_/¯
# note to future self - go here if you want to remember this: 
# https://github.com/davidgohel/officedown/discussions/103

footer_default <- block_list(
  fpar(
    run_word_field(field = "PAGE"),
    fp_p = fp_par(text.align = "left") 
  )
)

# Code in this chunk sets the margins for your document. 
# The helper functions page_long_above() and page_wide_above()
# also provide shortcuts for switching between wide (landscape)
# and normal (long) MS word layouts. 

# helper function for defining margins
make_margin <- function(x=NULL){
  
  if(is.null(x)){ return(page_mar()) } 
  
  if(is.character(x)){
    
    out <- switch(
      tolower(x),
      "normal" = page_mar(1, 1, 1, 1),
      "narrow" = page_mar(1/2, 1/2, 1/2, 1/2),
      "moderate" = page_mar(1, 1, 3/4, 3/4)
    )
    
  }
  
}

# set content above to be portrait
page_long_above <- function(margins = make_margin('narrow')){
  
  # b/c block_sections apply to content ABOVE, we set
  # the content BELOW to be landscape when we use page_long_above  
  set_fig_landscape()
  
  block_section(
    prop_section(
      page_size = page_size(orient = "portrait"),
      type = "continuous",
      page_margins = margins,
      footer_default = footer_default
    )
  )
  
}

# set content above to be landscape
page_wide_above <- function(margins = make_margin('narrow')){
  
  # b/c block_sections apply to content ABOVE, we set
  # the content BELOW to be portrait when we use page_wide_above
  set_fig_portrait()
  
  block_section(
    prop_section(
      page_size = page_size(orient = "landscape"),
      type = "continuous",
      page_margins = margins,
      footer_default = footer_default
    )
  )
  
}

```

```{r setup-targets}

withr::with_dir(
  new = here::here(),
  code = {
    targets::tar_load(names = c(data, meta, stats))
  }
)

```


```{r setup-dictionary}

# As the default dictionary, meta is applied to translate_ functions without
# needing to be explicitly supplied in the dictionary argument.
set_default_dictionary(meta)

```



```{r setup-formatters}

# make a short name for periglue::peri_value - this makes
# the inline reporting of results less complicated to read.
tv <- periglue::peri_value
tg <- periglue::peri_glue

r_version <- tg("{version$major}.{version$minor}")

```

```{r setup-tables}

# abbreviation management

abbrvs <- list(
  CI   = 'confidence interval',
  SD   = 'standard deviation',
  IQR  = 'interquartile range',
  EHR  = 'electronic health records',
  CVD  = 'cardiovascular disease',
  mm   = 'millimeters'
)

abbrvs_paste <- function(strings){
  
  front <- 'Abbreviations'
  
  matter <- glue::glue_collapse(strings, sep = '; ', last = '; and ')
  
  paste(front, matter, sep = ': ')
  
}

abbrvs_write <- function(abbr){
  
  sorted <- abbr[sort(names(abbr))]
  
  strings <- map2_chr(names(sorted), sorted, paste, sep = ' = ')
  
  abbrvs_paste(strings)
  
}


```

\newpage

Essentials for writing text are shown here. Demonstrations include creating a section and subsection, writing items in a bulleted list, citing items that are defined in `refs.bib`, and inserting R objects into the text.

# Section

A bulleted list:

- Results were produced with R version `r r_version`.[@r_language]

- Here's how to cite two or more things.[@orsf_aoas; @aorsf_joss; @aorsf_jcgs]

## Subsection

Here's how to put some results into the text: A total of `r tv(stats$.overall$nobs)` were included in the current analysis. The mean bill length was `r tv(stats$.overall$mean_bill_length)`. The mean (standard deviation) body mass was `r with(stats$.overall, tg("{mean_mass} ({sd_mass})"))`

# References

In case they are needed.

<div id="refs"></div>

\newpage

# Tables

A good convention is to make each table a sub section. This makes the table easier to find from the table of contents and also from the built-in Rstudio navigator. Another good convention is to start a new page for each table (use the `\newpage` command)

\newpage



## Table 1: Penguin characteristics

```{r}

footer_tbl_val <- "Table values are n (%) or median (25th, 75th percentile)"

data %>% 
  translate_data(dictionary = meta, units = 'descriptive') %>% 
  tbl_summary(by = 'island', missing = 'no') %>% 
  modify_footnote(c(all_stat_cols()) ~ NA) %>% 
  as_flex_table() %>% 
  theme_box() %>% 
  add_footer_lines(footer_tbl_val) %>% 
  align(j = c(2,3,4), align = 'center', part = 'all')

```

\newpage

## Table 2: A more customized table

```{r}

data %>% 
  group_by(species) %>% 
  slice(1:3) %>% 
  select(-body_mass_g, -sex, -year) %>% 
  mutate(across(where(is.numeric), peri_value)) %>% 
  as_grouped_data(groups = 'species') %>% 
  # translate after as_grouped_data, b/c as_grouped_data can
  # wipe away attributes, which will delete your labels.
  translate_data(dictionary = meta, units = 'descriptive') %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  padding(part = 'body', j = 1, i = ~ is.na(species),
          padding.left = 10) %>% 
  add_header_row(values = c(" ", " Penguin characteristics"),
                 colwidths = c(1, 3)) %>% 
  footnote(i = 2, j = 2, 
           part = 'header',
           value = as_paragraph("Bill length is measured using a ruler"),
           ref_symbols = '1') %>% 
  footnote(i = 1, j = 1, 
           part = 'body',
           value = as_paragraph('Adelies know they are a crowd favorite'), 
           ref_symbols = '2') %>% 
  theme_box() %>% 
  flextable_autofit(width_max = 5) %>% 
  flextable_polish(footer_text = abbrvs_write(abbrvs['mm']))

```


<!-- new page not needed at the end of a block section -->

`r page_long_above()`

To make a landscape section, use the block_section code here. Note that the section will be applied to all content prior to the block reaching up to the most recent block.

`r page_wide_above()`

To switch back to regular portrait section, add another portrait block. Notice how the block below acts on all content above it up to the prior block.

\newpage

# Figures

The default figure margins are set by the `page_long_above()` and `page_wide_above()`. You can change those to your preference by either modifying the functions or by setting `fig.width` and `fig.height` in the code chunk that prints the figure.

\newpage

## Figure 1: Penguin dimensions (normal version)

```{r}

fig <- ggplot(data = data) + 
  aes(x = bill_length_mm, y = bill_depth_mm, color = species) + 
  geom_point()

fig

```

There is a `theme_set()` command at the beginning of the document that sets our preferred `ggplot` theme. It aims to use the same font family and font size in the plots as is used in the text. I recommend changing the `ggplot` theming if you decide to use a different style for the word doc. If you want to just lightly modify the theme for specific plots, you can use the `theme()` function to add your flair. 

`r page_long_above()`

## Figure 2: Penguin dimensions (wide version)

```{r}

fig + 
  theme(panel.border = element_blank())

```

Hang on, how did the figure size change? That is an intended side effect of `page_long_above()` and `page_wide_above()`. Notably, if you ever want to avoid this convenient side effect, you can override it by setting `fig.width = X` and `fig.height = Y` where X and Y are your preferred figure width and height, in inches.

`r page_wide_above()`
