---
title: "Perisphere RWE Template"
format:
  revealjs:
    theme: simple
    css: slides/perisphere-slides.css
    bibliography: slides/refs.bib
    csl: slides/refs.csl
    slide-number: true
    logo: "slides/perisphere-logo.png"
    embed-resources: true
---

```{r setup-knitr, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,    # don't show code blocks
  message = FALSE, # don't print messages to the doc
  warning = FALSE, # don't print warnings to the doc
  dpi = 300,       # higher dpi => higher render time 
  fig.height = 6,  # default height is 6 inches
  fig.width = 10   # default width is 10 inches 
)

# Hello! This is the template word document for Perisphere reports.
# There are several code chunks used to set up the format of the
# document below. You don't have to modify those unless you want 
# to change the format of your output. 

```

```{r setup-pkgs}

# packages are usually handled by packages.R (in main directory).
# When tar_make() is run, it loads everything in packages.R.
# Assuming this document is in the list of targets (see ?tar_render),
# you won't need to include the library calls below.
# however, the template includes packages in its initial form
# so that you can knit the document without having to run tar_make().

# standards for word docs
library(officer)
library(flextable)

# specify a rounding specification 
library(table.glue)

# general purpose
library(tidyverse)
library(pericircle)

# table 1
library(gtsummary)

```

```{r setup-targets}

withr::with_dir(
  new = here::here(),
  code = {
    targets::tar_load(names = c(data, meta, stats))
  }
)

```

```{r setup-dictionary}

# As the default dictionary, meta is applied to translate_ functions without
# needing to be explicitly supplied in the dictionary argument.
set_default_dictionary(meta)

```

```{r setup-formatters}

# make a short name for table.glue::table_value - this makes
# the inline reporting of results less complicated to read.
tv <- table.glue::table_value
tg <- table.glue::table_glue

r_version <- tg("{version$major}.{version$minor}")

```

```{r setup-tables}

# abbreviation management

abbrvs <- list(
  CI   = 'confidence interval',
  SD   = 'standard deviation',
  IQR  = 'interquartile range',
  EHR  = 'electronic health records',
  CVD  = 'cardiovascular disease'
)

abbrvs_paste <- function(strings){
  
  front <- 'Abbreviations'
  
  matter <- glue::glue_collapse(strings, sep = '; ', last = '; and ')
  
  paste(front, matter, sep = ': ')
  
}

abbrvs_write <- function(abbr){
  
  sorted <- abbr[sort(names(abbr))]
  
  strings <- map2_chr(names(sorted), sorted, paste, sep = ' = ')
  
  abbrvs_paste(strings)
  
}


```


Essentials for writing text are shown here. Demonstrations include creating a section and subsection, writing items in a bulleted list, citing items that are defined in `refs.bib`, and inserting R objects into the text.

# Section

A bulleted list:

- Results were produced with R version `r r_version`.[@r_language]

- Here's how to cite two or more things.[@orsf_aoas; @aorsf_joss; @aorsf_jcgs]

## Subsection

Here's how to put some results into the text: A total of `r tv(stats$.overall$nobs)` were included in the current analysis. The mean bill length was `r tv(stats$.overall$mean_bill_length)`. The mean (standard deviation) body mass was `r with(stats$.overall, tg("{mean_mass} ({sd_mass})"))`

# References

In case they are needed.

<div id="refs"></div>



# Tables

A convention worth following is to make each table a sub section. This makes the table easier to find from the table of contents and also from the built-in Rstudio navigator.





## Table 1: Penguin characteristics

```{r}

footer_tbl_val <- "Table values are n (%) or median (25th, 75th percentile)"

data %>% 
  translate_data(meta, units = 'descriptive') %>% 
  tbl_summary(by = 'island', missing = 'no') %>% 
  modify_footnote(c(all_stat_cols()) ~ NA) %>% 
  as_flex_table() %>% 
  theme_box() %>% 
  add_footer_lines(footer_tbl_val) %>% 
  align(j = c(2,3,4), align = 'center', part = 'all')

```



## Table 2: A more customized table

```{r}

data %>% 
  group_by(species) %>% 
  slice(1:3) %>% 
  select(-body_mass_g, -sex, -year) %>% 
  mutate(across(where(is.numeric), table_value)) %>% 
  as_grouped_data(groups = 'species') %>% 
  # infuse after as_grouped_data, b/c as_grouped_data can
  # wipe away attributes, which will delete your labels.
  translate_data(meta, units = 'descriptive') %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(values = c(" ", " Penguin things"),
                 colwidths = c(1, 3)) %>% 
  bg(i = ~!is.na(species), bg = 'grey90') %>% 
  width(width = 1.5) %>% 
  width(j = 1, width = 2) %>% 
  align(part = 'all', j = c(2,3,4), align = 'center') %>% 
  footnote(i = 2, j = 2, 
           part = 'header',
           value = as_paragraph("Chinstraps boast the highest average bill length."),
           ref_symbols = '1') %>% 
  footnote(i = 1, j = 1, 
           part = 'body',
           value = as_paragraph('Adelies know they are a crowd favorite'), 
           ref_symbols = '2') %>% 
  add_footer_lines(values = abbrvs_write(abbrvs[c('CI', 'EHR', 'SD')])) %>% 
  add_footer_lines(values = "none of those abbreviations are in the table but they demonstrate how to include abbreviations using my helper functions")

```

# Figures

The default figure margins are set in the `setup-knitr`. You can change those to your preference by either modifying the call to `knitr::opt_chunk$set()` or by setting `fig.width` and `fig.height` in the code chunk that prints the figure.

## Figure 1: Penguin dimensions

```{r}

fig <- ggplot(data = data) + 
  aes(x = bill_length_mm, y = bill_depth_mm, color = species) + 
  geom_point()

fig

```

